Software Ticket Quality

### 2017-10-19 proposal/mprop.tex
Added paper on automatic bug report assigning

>>>>

\textbf{Bug Report Assignee Recommendation using 
Activity Profiles}\cite{Naguib2013BugReportAssignee}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper is to automatically detect who should be
    the developers who are most suitable to solve a specific issue.
  \item \textbf{What was the method?}
    They employed an algorithm using activity profiles (i.e.\ assign, review,
    resolve activity of the developer) such that, after detecting the prior
    experience, developer's role, and involvement in the project, it could
    recommend who should fix a specific bug. The average accuracy was around
    88\%, much higher than the LDA-SVM technique.
  \item \textbf{What did they learn?}
    They found out that their approach was more accurate than previous work
    done on assignee recommendation, but they think that it might even be
    improved further by combining their technique with the classic LDA-SVM one.
  \item \textbf{Relevance to our work}: this work complements the research
    presented in Anvik et al. \cite{anvik2006should} and it will provide us
    with valuable insight into how automatic triaging should be performed.
\end{itemize}
